On exponential sums arising from the classical doubling method

### 2025-03-04 paper.tex
Gauss sums are now Jacobi sums

\documentclass[12pt, reqno]{amsart}

@@

\newcommand{\parabolicSection}{\Phi^{\left(z_1, \dots, z_c\right)}}
\newcommand{\intertwiningOperator}{M^{\left(z_1, \dots, z_c\right)}}
\newcommand{\holomorphicRepresentation}{\depthZeroRepresentation^{\left(z_1, \dots, z_c\right)}}
\newcommand{\WhittakerFunctional}[1]{\ell_{#1, \fieldCharacter}}
\newcommand{\gWhittakerFunctional}[2]{\ell_{#1, #2}}
\newcommand{\gSpehWhittakerFunctional}[3]{\ell_{\SpehRepresentation{#1}{#3}, \fieldCharacter_{\UnipotentRadicalForWss{#2}{#3}}}}
\newcommand{\gShortSpehWhittakerFunctional}[3]{\ell_{\SpehRepresentation{#1}{#3}}}
\newcommand{\GaussSum}[2]{\mathcal{G}\left(#1, #2\right)}
\newcommand{\dblGaussSum}[2]{\mathcal{G}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\GaussSumScalar}[2]{\mathrm{G}\left(#1, #2\right)}
\newcommand{\dblGaussSumScalar}[2]{\mathrm{G}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblVirtualGaussSumScalar}[2]{\mathrm{g}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblGammaFactor}[3]{\Gamma^{\mathrm{dbl}}\left(#1 \times #2, #3\right)}
\newcommand{\dblGammaFactorSpace}[4]{\Gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\GKGaussSum}[3]{\mathcal{G}\left(#1 \times #2, #3\right)}
\newcommand{\GKGaussSumScalar}[3]{\mathrm{G}\left(#1 \times #2, #3\right)}
\newcommand{\fieldCharacterkc}[2]{\fieldCharacter_{\left({#2}^{#1}\right)}}
\newcommand{\ExoticKloosterman}{\mathrm{Kl}}
\newcommand{\GaussSumCharacter}[3]{\tau\left(#1 \times #2, #3\right)}
\newcommand{\IrrCusp}{\Irr_{\mathrm{cusp}}}
\newcommand{\convolutionWithCompactSupport}{\boldsymbol{\mathrm{R}}}
\newcommand{\ladicnumbers}{\algebraicClosure{\mathbb{Q}_{\ell}}}
\newcommand{\artinScrier}{\operatorname{AS}}
\newcommand{\KloostermanSumClassFunction}{\mathcal{K}}
\newcommand{\IsometryGroup}{\mathrm{Isom}}
\newcommand{\lieAlgebra}{\mathfrak{g}}
\newcommand{\DeligneLusztigInduction}[2]{\mathrm{R}_{#1}^{#2}}
\newcommand{\algebraicGroup}[1]{\boldsymbol{\mathrm{#1}}}
\newcommand{\LusztigSeries}[2]{\mathcal{E}\left(#1, (#2)\right)}
\newcommand{\ToriDualToriIsomorphism}{\kappa}
\newcommand{\characteristicPolynomial}{\operatorname{CharPoly}}

@@

\hypersetup{pdfauthor={Calvin Yost-Wolff, Elad Zelingher},
	pdfsubject={Number theory, Representation theory},
	pdfkeywords={Kloosterman sums, Gauss sums}}

@@

\subsection{TODO list}
\calvin{I mentioned this to Charlotte and will meet with her sometime after Arizona to discuss specifically the DL stuff to make sure that it ok. So we could try to have a draft }
\begin{enumerate}
	\item (Minor) Change terminology of Gauss sums $\dblGaussSumScalar{\pi}{\chi}$ to Jacobi sums and the notation to $J^{\mathrm{dbl}}\left(\pi, \chi\right)$ as they are similar to the Jacobi sums
	$$J\left(\alpha, \beta\right) = \sum_{\substack{x,y \in \multiplicativegroup{\finiteField}\\
	x+y = 1}} \alpha\left(x\right) \beta\left(y\right),$$
	compare with $$\dblGaussSumScalar{\pi}{\chi} = \sum_{\substack{g \in G\\
			h \in \GL\left(\hermitianSpace\right)\\
	g + h = \idmap_{\hermitianSpace}}} \pi\left(g\right) \chi\left(\det\left(-h\right)\right).$$
	Consider replacing $\chi\left(\det\left(g - \idmap_{\hermitianSpace}\right)\right)$ with $\chi\left(\det\left(\idmap_{\hermitianSpace} - g\right)\right)$ for aesthetics (probably not worth it).
	\item Maybe define the algebraic group versions $\algebraicGroup{G}$ and $\GroupExtension{\algebraicGroup{G}}$ in Section 3.2. For instance for $\algebraicGroup{\Sp}_{2n}$ we can define
	$$\algebraicGroup{\tilde{G}} = \left\{ \left(g,\lambda\right) \in \algebraicGroup{\GL}\left(\hermitianSpace\right) \times \multiplcativeScheme \mid \involution{\transpose{g}} J g = \lambda J,\ \right\}$$ for suitable $J$ and then define the torus $\algebraicGroup{S}$ that appears in \cite[Page 140]{DigneMichel2020} as $$\algebraicGroup{S} = \left\{\left(\begin{pmatrix}
		t \IdentityMatrix{n}\\
		& \IdentityMatrix{n}
	\end{pmatrix}, t\right) \mid t \in \multiplcativeScheme \right\} \subset \GroupExtension{\algebraicGroup{G}}.$$
	\item In the computations of $\dblGammaFactor{\pi}{\chi}{\fieldCharacter}$ in terms of Deligne--Lusztig we should say that when we take a torus of $\GroupExtension{G}$ and intersect it with $G$ we get a torus of $G$ and hence it suffices to compute whatever we are computing.
	\item The proof of \Cref{prop:gamma-factor-is-constant-on-lusztig-series} should be modified. We should first use $\GroupExtension{G}$. For this group we have the ``at most one cuspidal'' property. Then we should use \cite[Page 140]{DigneMichel2020} $$R_{\GroupExtension{T}}^{\GroupExtension{G}}\left(\tilde{\theta}\right) \restriction_{G} = R_{T}^G \left(\tilde{\theta}\restriction_{T}\right),$$
	where we need to explain the notation.
	\item \Cref{subsec:tori-isomorphism} and \Cref{subsec:gauss-sums-attached-to-semi-simple} should be removed and replaced with Calvin's arguments.
\end{enumerate}

@@

\section{Doubling method Gauss sums}

@@

Given an irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$, we consider the following \emph{doubling method Gauss sum}:
$$\dblGaussSum{\tau}{\chi} = q^{-\frac{k^2}{2}} \sum_{g \in \GL_k\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \tau\left(g\right).$$
Then $\dblGaussSum{\tau}{\chi}$ defines an element of $\Hom_{\GL_k\left(\finiteField\right)}\left(\tau, \tau\right)$. Therefore, by Schur's lemma there exists a complex number $\dblGaussSumScalar{\tau}{\chi} \in \cComplex$ such that $$\dblGaussSum{\tau}{\chi} = \dblGaussSumScalar{\tau}{\chi} \cdot \idmap_\tau.$$

The goal of this section is to express $\dblGaussSumScalar{\tau}{\chi}$ in terms of Kondo's Gauss sum.

@@

We now use this to compute $\dblGaussSum{\tau}{\chi}$. We have that $$\dblGaussSum{\tau}{\chi} = q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \pi\left(-y^{-1} x\right).$$
The last equality implies the following result.
\begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
	$$\dblGaussSumScalar{\tau}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
\end{theorem}

@@

Let $\pi$ be an irreducible representation of $H$ where $H \in \{G, \GroupExtension{G}\}$. Denote $$\dblGaussSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \Phi_{\chi}\left(g\right).$$
Since $\Phi_{\chi}$ is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$, it is also a class function of $G$. Since $G$ is a normal subgroup of $H$, we have that $\dblGaussSum{\pi}{\chi} \in \Hom_{H}\left(\pi, \pi\right)$. By Schur's lemma, there exists a constant $\dblGaussSumScalar{\pi}{\fieldCharacter} \in \cComplex$, such that $$\dblGaussSum{\pi}{\chi} = \dblGaussSumScalar{\pi}{\chi} \cdot \idmap_\pi.$$
We call $\dblGaussSumScalar{\pi}{\chi}$ the \emph{doubling method Gauss sum}.

\subsubsection{Multiplicativity property}
Our next goal is to understand how the doubling method Gauss sum behaves under parabolic induction.

@@

\begin{theorem}\label{thm:multiplicativity-in-terms-of-gauss-sums}
	Let $\pi'$ be an irreducible representation of $H'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\quadraticExtension\right)$. Then for any irreducible representation $\pi$ of $H$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{H}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\involutionPlusOne{\chi} \ne 1$, we have
	$$\dblGaussSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\involutionPlusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}^k \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter_{\quadraticExtension}} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter_{\quadraticExtension}} \dblGaussSumScalar{\pi'}{\chi}.$$
\end{theorem}
\begin{proof}
	Let $v_{\pi'} \in \pi'$ and $v_{\tau} \in \tau$. Consider $f \in \rho$ defined as follows. The function $f \in \rho$ is the unique element supported on $P$, such that $f\left(\idmap_{\hermitianSpace}\right) = v_{\tau} \otimes v_{\pi'}$. The projection $f$ to any non-zero invariant subspace of $\rho$ is non-zero. We compute $\dblGaussSum{\rho}{\chi} f$.

	Notice that for $x \in G$, $$\left(\dblGaussSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \Phi_{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \Phi_{\chi}\left(x^{-1} p\right),$$
	which can be rewritten as
	$$\left(\dblGaussSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \Phi_{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
	As before, we may write
	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic h\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h^{-1}\right)\right)\right).$$
	Hence, \begin{align*}
		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(Ah\right)\right) \\
		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	Assume that $\chi \ne 1$. By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$. Let us replace $h$ with $A^{-1} h$. We get the sum
	\begin{align*}
		\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right) \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A x l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
	The inner sum over $N$ will vanish unless $Ax \in P$. Thus we have
	\begin{align*}
		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left(p - x^{-1}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	By decomposing the sum over $p' \in P$ into a sum over $N$ and $L$, we see that the inner sum over $N$ will vanish unless $p - x^{-1} \in P$, which implies that $x \in P \cap G$.

>>>>

\documentclass[12pt, reqno]{amsart}
\usepackage[normalem]{ulem}

@@

\newcommand{\parabolicSection}{\Phi^{\left(z_1, \dots, z_c\right)}}
\newcommand{\intertwiningOperator}{M^{\left(z_1, \dots, z_c\right)}}
\newcommand{\holomorphicRepresentation}{\depthZeroRepresentation^{\left(z_1, \dots, z_c\right)}}
\newcommand{\WhittakerFunctional}[1]{\ell_{#1, \fieldCharacter}}
\newcommand{\gWhittakerFunctional}[2]{\ell_{#1, #2}}
\newcommand{\gSpehWhittakerFunctional}[3]{\ell_{\SpehRepresentation{#1}{#3}, \fieldCharacter_{\UnipotentRadicalForWss{#2}{#3}}}}
\newcommand{\gShortSpehWhittakerFunctional}[3]{\ell_{\SpehRepresentation{#1}{#3}}}
\newcommand{\GaussSum}[2]{\mathcal{G}\left(#1, #2\right)}
\newcommand{\dblJacobiSum}[2]{\mathcal{J}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\GaussSumScalar}[2]{\mathrm{G}\left(#1, #2\right)}
\newcommand{\dblJacobiSumScalar}[2]{\mathrm{J}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblVirtualJacobiSumScalar}[2]{\mathrm{j}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblGammaFactor}[3]{\Gamma^{\mathrm{dbl}}\left(#1 \times #2, #3\right)}
\newcommand{\dblGammaFactorSpace}[4]{\Gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\GKGaussSum}[3]{\mathcal{G}\left(#1 \times #2, #3\right)}
\newcommand{\GKGaussSumScalar}[3]{\mathrm{G}\left(#1 \times #2, #3\right)}
\newcommand{\fieldCharacterkc}[2]{\fieldCharacter_{\left({#2}^{#1}\right)}}
\newcommand{\ExoticKloosterman}{\mathrm{Kl}}
\newcommand{\GaussSumCharacter}[3]{\tau\left(#1 \times #2, #3\right)}
\newcommand{\IrrCusp}{\Irr_{\mathrm{cusp}}}
\newcommand{\convolutionWithCompactSupport}{\boldsymbol{\mathrm{R}}}
\newcommand{\ladicnumbers}{\algebraicClosure{\mathbb{Q}_{\ell}}}
\newcommand{\artinScrier}{\operatorname{AS}}
\newcommand{\KloostermanSumClassFunction}{\mathcal{K}}
\newcommand{\IsometryGroup}{\mathrm{Isom}}
\newcommand{\lieAlgebra}{\mathfrak{g}}
\newcommand{\DeligneLusztigInduction}[2]{\mathrm{R}_{#1}^{#2}}
\newcommand{\algebraicGroup}[1]{\boldsymbol{\mathrm{#1}}}
\newcommand{\LusztigSeries}[2]{\mathcal{E}\left(#1, (#2)\right)}
\newcommand{\ToriDualToriIsomorphism}{\kappa}
\newcommand{\characteristicPolynomial}{\operatorname{CharPoly}}

@@

\hypersetup{pdfauthor={Calvin Yost-Wolff, Elad Zelingher},
	pdfsubject={Number theory, Representation theory},
	pdfkeywords={Kloosterman sums, Exponential sums}}

@@

\subsection{TODO list}
\calvin{I mentioned this to Charlotte and will meet with her sometime after Arizona to discuss specifically the DL stuff to make sure that it ok. So we could try to have a draft }
\begin{enumerate}
	\item (Minor) \sout{Change terminology of Gauss sums $\dblJacobiSumScalar{\pi}{\chi}$ to Jacobi sums and the notation to $J^{\mathrm{dbl}}\left(\pi, \chi\right)$ as they are similar to the Jacobi sums}
	$$J\left(\alpha, \beta\right) = \sum_{\substack{x,y \in \multiplicativegroup{\finiteField}\\
	x+y = 1}} \alpha\left(x\right) \beta\left(y\right),$$
	compare with $$\dblJacobiSumScalar{\pi}{\chi} = \sum_{\substack{g \in G\\
			h \in \GL\left(\hermitianSpace\right)\\
	g + h = \idmap_{\hermitianSpace}}} \pi\left(g\right) \chi\left(\det\left(-h\right)\right).$$
	Consider replacing $\chi\left(\det\left(g - \idmap_{\hermitianSpace}\right)\right)$ with $\chi\left(\det\left(\idmap_{\hermitianSpace} - g\right)\right)$ for aesthetics (probably not worth it).
	\item Maybe define the algebraic group versions $\algebraicGroup{G}$ and $\GroupExtension{\algebraicGroup{G}}$ in Section 3.2. For instance for $\algebraicGroup{\Sp}_{2n}$ we can define
	$$\algebraicGroup{\tilde{G}} = \left\{ \left(g,\lambda\right) \in \algebraicGroup{\GL}\left(\hermitianSpace\right) \times \multiplcativeScheme \mid \involution{\transpose{g}} J g = \lambda J,\ \right\}$$ for suitable $J$ and then define the torus $\algebraicGroup{S}$ that appears in \cite[Page 140]{DigneMichel2020} as $$\algebraicGroup{S} = \left\{\left(\begin{pmatrix}
		t \IdentityMatrix{n}\\
		& \IdentityMatrix{n}
	\end{pmatrix}, t\right) \mid t \in \multiplcativeScheme \right\} \subset \GroupExtension{\algebraicGroup{G}}.$$
	\item In the computations of $\dblGammaFactor{\pi}{\chi}{\fieldCharacter}$ in terms of Deligne--Lusztig we should say that when we take a torus of $\GroupExtension{G}$ and intersect it with $G$ we get a torus of $G$ and hence it suffices to compute whatever we are computing.
	\item The proof of \Cref{prop:gamma-factor-is-constant-on-lusztig-series} should be modified. We should first use $\GroupExtension{G}$. For this group we have the ``at most one cuspidal'' property. Then we should use \cite[Page 140]{DigneMichel2020} $$R_{\GroupExtension{T}}^{\GroupExtension{G}}\left(\tilde{\theta}\right) \restriction_{G} = R_{T}^G \left(\tilde{\theta}\restriction_{T}\right),$$
	where we need to explain the notation.
	\item \Cref{subsec:tori-isomorphism} and \Cref{subsec:gauss-sums-attached-to-semi-simple} should be removed and replaced with Calvin's arguments.
\end{enumerate}

@@

\section{Doubling method Jacobi sums}

@@

Given an irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$, we consider the following \emph{doubling method Jacobi sum}:
$$\dblJacobiSum{\tau}{\chi} = q^{-\frac{k^2}{2}} \sum_{g \in \GL_k\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \tau\left(g\right).$$
Then $\dblJacobiSum{\tau}{\chi}$ defines an element of $\Hom_{\GL_k\left(\finiteField\right)}\left(\tau, \tau\right)$. Therefore, by Schur's lemma there exists a complex number $\dblJacobiSumScalar{\tau}{\chi} \in \cComplex$ such that $$\dblJacobiSum{\tau}{\chi} = \dblJacobiSumScalar{\tau}{\chi} \cdot \idmap_\tau.$$

The goal of this section is to express $\dblJacobiSumScalar{\tau}{\chi}$ in terms of Kondo's Gauss sum.

@@

We now use this to compute $\dblJacobiSum{\tau}{\chi}$. We have that $$\dblJacobiSum{\tau}{\chi} = q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \pi\left(-y^{-1} x\right).$$
The last equality implies the following result.
\begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
	$$\dblJacobiSumScalar{\tau}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
\end{theorem}

@@

Let $\pi$ be an irreducible representation of $H$ where $H \in \{G, \GroupExtension{G}\}$. Denote $$\dblJacobiSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \Phi_{\chi}\left(g\right).$$
Since $\Phi_{\chi}$ is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$, it is also a class function of $G$. Since $G$ is a normal subgroup of $H$, we have that $\dblJacobiSum{\pi}{\chi} \in \Hom_{H}\left(\pi, \pi\right)$. By Schur's lemma, there exists a constant $\dblJacobiSumScalar{\pi}{\fieldCharacter} \in \cComplex$, such that $$\dblJacobiSum{\pi}{\chi} = \dblJacobiSumScalar{\pi}{\chi} \cdot \idmap_\pi.$$
We call $\dblJacobiSumScalar{\pi}{\chi}$ the \emph{doubling method Jacobi sum}.

\subsubsection{Multiplicativity property}
Our next goal is to understand how the doubling method Jacobi sum behaves under parabolic induction.

@@

\begin{theorem}\label{thm:multiplicativity-in-terms-of-gauss-sums}
	Let $\pi'$ be an irreducible representation of $H'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\quadraticExtension\right)$. Then for any irreducible representation $\pi$ of $H$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{H}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\involutionPlusOne{\chi} \ne 1$, we have
	$$\dblJacobiSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\involutionPlusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}^k \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter_{\quadraticExtension}} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter_{\quadraticExtension}} \dblJacobiSumScalar{\pi'}{\chi}.$$
\end{theorem}
\begin{proof}
	Let $v_{\pi'} \in \pi'$ and $v_{\tau} \in \tau$. Consider $f \in \rho$ defined as follows. The function $f \in \rho$ is the unique element supported on $P$, such that $f\left(\idmap_{\hermitianSpace}\right) = v_{\tau} \otimes v_{\pi'}$. The projection $f$ to any non-zero invariant subspace of $\rho$ is non-zero. We compute $\dblJacobiSum{\rho}{\chi} f$.

	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \Phi_{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \Phi_{\chi}\left(x^{-1} p\right),$$
	which can be rewritten as
	$$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \Phi_{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
	As before, we may write
	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic h\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h^{-1}\right)\right)\right).$$
	Hence, \begin{align*}
		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(Ah\right)\right) \\
		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	Assume that $\chi \ne 1$. By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$. Let us replace $h$ with $A^{-1} h$. We get the sum
	\begin{align*}
		\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right) \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A x l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
	The inner sum over $N$ will vanish unless $Ax \in P$. Thus we have
	\begin{align*}
		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left(p - x^{-1}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
	\end{align*}
	By decomposing the sum over $p' \in P$ into a sum over $N$ and $L$, we see that the inner sum over $N$ will vanish unless $p - x^{-1} \in P$, which implies that $x \in P \cap G$.

	Hence, we have that $\dblJacobiSum{\rho}{\chi} f$ is supported on $P$. We move to compute $\left(\dblJacobiSum{\rho}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
	\begin{equation}\label{eq:recursive-doubling-gauss-sum}
		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P \cap G\\
				\detQuadratic\left(p - \idmap_{\hermitianSpace}\right) \ne 0}} \chi\left(\detQuadratic\left(p - \idmap_{\hermitianSpace}\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
	\end{equation}
	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(p - \idmap_{\hermitianSpace}\right) = \left(-1\right)^k \detQuadratic\left(\involution{a}\right)^{-1}\detQuadratic\left(a - \IdentityMatrix{k}\right) \det\left(\involution{\left(a - \IdentityMatrix{k}\right)}\right) \detQuadratic\left( g' - \idmap_{\hermitianSpace'}\right),$$
	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
	we get that \eqref{eq:recursive-doubling-gauss-sum} equals
	\begin{equation}
		\chi\left(-1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \Phi_{\involutionPlusOne{\chi}}\left(a\right) \minusInvolution{\chi}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
	\end{equation}
	which in turn is
	\begin{align*}
		&\chi\left(-1\right)^k \dblJacobiSum{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} v_{\tau} \otimes \dblJacobiSum{\pi'}{\chi} v_{\pi'}\\
		=& \chi\left(-1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
	\end{align*}
	The result now follows.
\end{proof}
